fdcoexist

### 2018-09-04 paper_simulations.Rmd
Run simulations for 500 generations

# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights,
                        time = 150) {

@@

# This function tidy a list of simulation routine to a single data.frame
# suitable to make figures.
tidy_simulation_list = function(simulation_list, set_of_traits, trait_scenarios,
                                time = 150, scenar_names = names(trait_scenarios)) {
    simulation_list %>%
        names() %>%
        # Tidy single simulations
        lapply(tidy_simulation,
               given_simul = simulation_list,
               given_traits = set_of_traits,
               given_trait_scenar = trait_scenarios,
               time = time) %>%
        # Re-add names
        set_names(nm = names(simulation_list)) %>%
        # Join into single data.frame
        bind_rows(.id = "scenario") %>%
        # Compute pre-CWMs
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, scenar_names))
}

tidy_simulation = function(scenario, given_simul, given_traits,
                           given_trait_scenar, time = 150) {
    landscape_df(given_simul[[scenario]], given_traits,
                 trait_scenarios[[scenario]], time = time) %>%
        inner_join(given_traits %>%
                       as.data.frame() %>%
                       rownames_to_column("species"),
                   by = "species") %>%
        group_by(patch) %>%
        mutate(rel_abund = N/sum(N)) %>%
        ungroup()
}
# Initial parameters -----------------------------------------------------------
suppressMessages(devtools::load_all())

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 150  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

>>>>

# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights,
                        time = n_gen) {

@@

# This function tidy a list of simulation routine to a single data.frame
# suitable to make figures.
tidy_simulation_list = function(simulation_list, set_of_traits, trait_scenarios,
                                time = n_gen, scenar_names = names(trait_scenarios)) {
    simulation_list %>%
        names() %>%
        # Tidy single simulations
        lapply(tidy_simulation,
               given_simul = simulation_list,
               given_traits = set_of_traits,
               given_trait_scenar = trait_scenarios,
               time = time) %>%
        # Re-add names
        set_names(nm = names(simulation_list)) %>%
        # Join into single data.frame
        bind_rows(.id = "scenario") %>%
        # Compute pre-CWMs
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, scenar_names))
}

tidy_simulation = function(scenario, given_simul, given_traits,
                           given_trait_scenar, time = n_gen) {
    landscape_df(given_simul[[scenario]], given_traits,
                 trait_scenarios[[scenario]], time = time) %>%
        inner_join(given_traits %>%
                       as.data.frame() %>%
                       rownames_to_column("species"),
                   by = "species") %>%
        group_by(patch) %>%
        mutate(rel_abund = N/sum(N)) %>%
        ungroup()
}
# Initial parameters -----------------------------------------------------------
suppressMessages(devtools::load_all())

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 500  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength
